\TheTitle

### 2016-04-24 linvis.tex
i have to go for lunch... back in couple of hours

Maintainers of older versions of the Linux kernel must sift through thousands of
commits with tools that are unable to filter and effectively visualize projects at
the scale of the kernel. Tools like Gitk use a directed acyclic graph (DAG) model,
showing all commits and merges in chronological order by when the commit was
authored. This representation works in smaller projects; it enables users to see
when changes are made, when these changes are merged, and how each branch is
interacting.  In large modular projects, like the Linux kernel, the DAG becomes a
mess of merges and commits (figure \ref{fig:gitk}) losing its visual meaning. In
some cases, the Linux kernel is simply too large for the system to generate a
visualization. Github provides a DAG view for many projects, but is unable to
display the visualization for projects as large as the Linux kernel (figure
\ref{fig:gitfail}).

@@

Git cannot store the date that a commit was merged into a branch due to the rebase
operation. A rebase can perform several changes to commits and merges. It may be
squashed with other commits, combining the effects of several commits into a single
commit. It may be dropped altogether, in which case the commit is no-longer merged.
It may be that the entire branch has simply been re-rooted to another position on
the DAG. Due to this, tools are unable to determine when a commit is merged. A user
may decide that it is important to be able to see only the commits contributing to a
given release, that is commits that were merged with the Linus-branch of the kernel
between two given dates. This operation is not possible without the collection of
additional data that is not provided by git. Git only enables users to see when a
commit was authored, not when it was merged into a branch.

@@

>>>>

Maintainers of older versions of the Linux kernel (such as those used in embedded systems and mobile phones) must keep track of changes to the current version
of the current in order to determine what commits are relevant to their versions.
Due to the ratio of growth of the kernel (every year, between 50 and 70 thousand commits get added to it)
this process requires
sifting through thousands of
commits with tools that are unable to filter and effectively visualize projects at
the scale of the kernel. Tools like Gitk use a directed acyclic graph (DAG) model,
showing all commits and merges in chronological order by when the commit was
authored, and not by then it arrives in the official repository.

This representation works in smaller projects; it enables users to see
when changes are made, when these changes are merged, and how each branch is
interacting.  
In large modular projects, like the Linux kernel, the DAG becomes a
mess of merges and commits (figure \ref{fig:gitk}) losing its visual meaning.  In
some cases, the Linux kernel is simply too large for the system to generate a
visualization (eg. Github provides a DAG view for many projects, but is unable to
display the visualization for projects as large as the Linux kernel (figure
\ref{fig:gitfail}).
Furthermore, Linux creates between 60 and 70k new commits every year and, according to \cite{emsePaper}, 
a commit a median of YYYY days to arrive to the official repository from the moment it is authored. 
This means that, if a person inspected the commits in this repository today, tomorrow it might contain  hundreds
of commits that were authored months ago. However, distinguishing these new commits is not trivial.

@@

One of the challenges with visualzing the arrival of commits to a repository is that
in Git, commits are immutable, and Git does not store the date that a commit was merged into another branch (including master)
To complicate the problem, the DAG points to the ancestors of a commit (a model necessary for the operation of Git), but developers 
would prefer to know the path that a commit followed to reach the master repository. \dmg{perhaps a figure is good here}.
In the context of Linux tracing the path that a commit followed to master would imply that for any given merge, it would be possible to know what commits were merged.
With such a feature,  a user
could inspect the commits that have arrived into master within a given time frame.
 and decide that it is important.

\dmg{I am going to describe the method we used here... }

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
